---
title       : Slidify the Shiny Application
subtitle    : Documentation for the Prediction of diamond price using Shiny
author      : Shaoqing Ying
job         : R
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github      :
  user: shaoqingy
  repo: slidify Shiny Application
---

## Project Overview

1. This is a simple shiny application for the project of coursera course "Developing Data Products".

2. The application aimts at predicting the diamond price according to its mass.

3. The regression model was chosen for the prediction based on the training of the data "diamond" from the package "UsingR".

4. You can find the application under the link: https://shaoqingy.shinyapps.io/myshinyapplication/

--- .class #id 

## Project Operation

1. On the left side, the diamond mass in carat could be chosen for prediction

2. On the right side, the graphic displays the real prices and predicted prices for different masses and also the linear regression.

3. The predicted price for the given mass would be shown in the graphic with black point.

4. The predicted price would also be shown below with numbers.

5. There is also a simple documentation for the application below. 

--- 

## Data for Modelling

```{r message=F, warning=F}
library(UsingR);data(diamond);head(diamond,3)
summary(diamond)
```

---

## Display Example

- The predicted price for the selected diamond mass of 0.2 carat is: 507.79 $

```{r message=F, warning=F, echo=F}
library(UsingR)
data(diamond)
    xcarat <- 0.2
    fit <- lm(price ~ carat-1, data = diamond)
    pred <- predict(fit, data.frame(carat = xcarat))
    plot(diamond$carat, diamond$price, xlab = "Mass (carats)", ylab = "Price (SIN $)",bg = "lightblue", col = "black", cex = 2, pch = 21)
    abline(fit, lwd = 2)
    points(diamond$carat, predict(fit), cex = 2, pch = 19, col = "red")
    points(xcarat, pred, cex = 4, pch = 19, col = "black")
```




